Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion

### 2018-09-29 outputs/docs/events/svm-rmarkdown-article-example.tex
GET TO DRAFT STAGE HOORAY

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 28
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent Government policy is partly driven by parliamentary discussion.
Conversely, that same discussion can indicate a government's priorities.
But major events--both expected, such as an election, and unexpected,
such as a recession or terrorist attack--can affect the course of
parliamentary discussion. In this paper, we systematically analyse how
parliamentary discussion changes in response to different types of
events in Australian history. We compile a dataset of what was said in
Australian state and federal parliaments from the mid-1800s through to
2017 based on available public records. We use a structural text model
to reduce the dimensionality of the text and to impose prior knowledge
such as correlation between days and changes over time. We then examine
the effect of various events using a simple discrete choice model. We
find that: 1) changes of government are associated with topic changes
only when there is also a change of the party in power; and 2) economic
events, such as financial crises, have significant and persistent
effects. Our findings have implications for how we think about the
longer-term trajectory of government policy as the media cycle becomes
increasingly focused on short-term events.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then use a discrete choice model
to examine changes at various types of events, including: changes in
government; changes in the political environment (as defined by polling
or other results); changes in economic conditions; and other significant
events (such as the 9/11 attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our use
of a discrete choice model allows us construct a counterfactual. Our
work fits into a growing literature that considers text as an input to
more usual quantitative techniques, rather than requiring separate
analysis. While using text as data has well-known shortcomings, it
allows larger-scale analysis that would not be viable using
less-automated approaches and so it can identify patterns that may
otherwise be overlooked.

@@

Following the example of the UK a daily text record called Hansard of
what was said in Australian parliaments has been made available since
their establishment.\footnote{While Hansard is not necessarily verbatim,
  it is considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians.} Earlier work on
the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
\textbf{{[}ANOTHER REFERENCE{]}}, often examined broader activity
measures. This allowed for long time frames and wide comparisons. But
Hansard records and their equivalents are an increasingly viable and
popular source of data as new methods and reduced computational costs
make larger-scale analysis easier.

The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
\citet{Whyte2017} to examine whether parliamentary disruptions in Canada
increased between 1926 and 2015 and \citet{RheaultCochran2018} to
examine ideology and party polarisation in Britain and Canada. In the
UK, \citet{Duthie2016} analysed Hansard records to examine which
politicians made supportive or aggressive statements toward other
politicians between 1979 and 1990 and \citet{PetersonSpirling2018}
examined polarisation. As digitisation methods improve increasingly
older UK records can be analysed, for instance \citet{Dimitruk2018}
considers the effect of estate bills on prorogations in seventeenth
century England. In New Zealand, \citet{Curran2017} modelled the topics
discussed between 2003 and 2016, and \citet{Graham2016} examined
unparliamentary language between 1890 and 1950. And in the US
\citet{GentzkowShapiroTaddy2018} examine congressional speech records
from 1873 to 2016 to find that partisanship has risen in the past few
decades.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
An example of what a page of Hansard looks like is included in Appendix
\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
available in some cases.\footnote{Tim Sherratt makes these XML records
  available as a single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
available across the state and federal parliaments (Table 1)
\textbf{{[}UPDATE NUMBERING{]}}. As with any larger-scale data process,
there are various issues with some of the PDFs and the known ones are
detailed in Appendix \textbf{{[}ADD NUMBERING{]}}.

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Number of records\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 &
7,873\tabularnewline
& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Queensland & Legislative Assembly & 1860 - 2017 & 9,699\tabularnewline
& Legislative Council & 1860 - 1922 & 4,156\tabularnewline
New South Wales\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.} & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Victoria & Legislative Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Tasmania & House of Assembly & 1856 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
South Australia & House of Assembly & 1857 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
Western Australia & Legislative Assembly & 1890 - 2017 &
\textbf{{[}TBD{]}}\tabularnewline
& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
\bottomrule
\end{longtable}

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
  NUMBERING{]}}. The full set of scripts are available on request.}
These scripts are primarily based on: the \texttt{PDFtools} package of
\citet{Ooms2018pdftools}; the \texttt{tidyverse} package of
\citet{Wickham2017}; the \texttt{tm} package of
\citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. The \texttt{hunspell} package of
\citet{Ooms2017} is also used to help find spelling issues.

These daily records are the main data used in this paper, however the
daily records are also further divided into individual-level records.
Sometimes these are just short interjections or notes that are not
specific to any particular politician, such as `Honourable members
interjecting'. The high dimensional nature of text data means that the
appropriate analysis dataset is research-question specific. For
instance, in our paper interjections are not important because they do
not usually contribute much to defining the topics being discussed. But
they are interesting in their own right and \citet{Whyte2017} analysed
them in a Canadian context for the period 1926 to 2015 to find that
female MPs were more likely to be interrupted than male MPs.

Usually the disaggregation into individual-level records is done by
identifying politicians' names in particular patterns. For instance,
when the Hansard record is trying to indicate that a person is speaking,
as opposed to being mentioned (for more on the political effect of being
mentioned see \citet{Alexander2018}), often the name is in upper case
(e.g. `Mr WHITLAM' or `Mr MENZIES'); followed by a dash or colon; or are
next to some title within brackets. There is substantial variation in
how the person making a statement is identified. Again some error is
introduced at this stage because of inconsistencies over time and
between the parliaments, as well as the errors introduced during the PDF
parsing stage. There is considerable variance but on average each daily
record had 250 \textbf{{[}UPDATE{]}} individual-level records, resulting
in roughly 15 million rows \textbf{{[}UPDATE{]}} across the state and
federal parliaments.

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
\textbf{{[}Need to bundle\_ngrams i.e.~olive oil is olive\_oil{]}}

@@

Data from other sources are useful to complement the parliamentary text
data. For instance, although the name, party, and division represented
are contained in Hansard records they are inconsistent. Also non-Hansard
information about the politicians can inform the analysis. This
includes: date of birth and date of death; sex; date of entry to
parliament and exit from parliament; some aspects of their pre- and
post-parliamentary career; some aspects of their parliamentary career,
such as ministry appointments; and electoral information such as primary
and two-party-preferred results.

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The
  datasets are available on request.}

@@

The main models that we use in this paper are the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
implemented by the \texttt{XXXX} R package of \textbf{XYZ}. In theory we
could have directly used the text as an input to the discrete choice
model, but this can become intractable. Instead, in a similar way to
\citet{MuellerRauh2018}, we use the topics that the text is about as an
input to another model, which in our case is a discrete choice model. In
Appendix \textbf{{[}ADD NUMBERING{]}}, we include an alternative
approach that follows \citet{Taddy2015} by using word2vec, which more
closely uses words, rather than topics, as an input.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section we provide a brief overview of
both the LDA model and the STM. we consider the outputs of the topic
model as reduced dimension inputs. In our case they are inputs to a
discrete choice model, and so we then discuss that model.

@@

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics. More generally, the
LDA topic model works by considering each document as having been
generated by some probability distribution over topics. For instance, if
there were five topics and two documents, then the first document may be
comprised mostly of the first few topics; the other document may be
mostly about the final few topics (Figure
\ref{fig:topicsoverdocuments}).

Similarly, each topic could be considered a probability distribution
over terms. To choose the terms used in each document the speaker picks
terms from each topic in the appropriate proportion. For instance, if
there were ten terms, then one topic could be defined by giving more
weight to terms related to immigration; and some other topic may give
more weight to terms related to the economy (Figure
\ref{fig:topicsoverterms}).

@@

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a common list
of stop words such as: ``a''; ``an''; and ``and''. However the exact
list used depends on research of focus. In the case of Australian
Hansard, these are words such as: ``australia''; ``australian''; and
``bill''. Punctuation and capitalisation is also typically removed. The
documents then need to then be transformed into a document-term-matrix.
This is essentially a table with a column of the number of times each
term appears in each document.

After the dataset is ready, the R \texttt{topicmodels} package of
\citet{Grun2011} can be used to implement LDA and approximate the
posterior. It can do this using Gibbs sampling or the variational
expectation-maximization algorithm. Following
\citet{SteyversGriffiths2006} and \citet{Darling2011}, the Gibbs
sampling process attempts to find a topic for a particular term in a
particular document, given the topics of all other terms for all other
documents. Broadly, it does this by first assigning every term in every
document to a random topic, specified by Dirichlet priors with
\(\alpha = \frac{50}{K}\) and \(\eta = 0.1\)
(\citet{SteyversGriffiths2006} recommends \(\eta = 0.01\)), where
\(\alpha\) refers to the distribution over topics and \(\eta\) refers to
the distribution over terms (\citet{Grun2011}, p.~7). It then selects a
particular term in a particular document and assigns it to a new topic
based on the conditional distribution where the topics for all other
terms in all documents are taken as given (\citet{Grun2011}, p.~6):
\[p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} \]
where \(z'_{d, n}\) refers to all other topic assignments;
\(\lambda'_{n\rightarrow k}\) is a count of how many other times that
term has been assigned to topic \(k\); \(\lambda'_{.\rightarrow k}\) is
a count of how many other times that any term has been assigned to topic
\(k\); \(\lambda'^{(d)}_{n\rightarrow k}\) is a count of how many other
times that term has been assigned to topic \(k\) in that particular
document; and \(\lambda'^{(d)}_{-i}\) is a count of how many other times
that term has been assigned in that document. Once \(z_{d,n}\) has been
estimated, then estimates for the distribution of words into topics and
topics into documents can be backed out.

The choice of the number of topics, \emph{k}, affects the results, and
must be specified \emph{a priori}. If there is a strong reason for a
particular number, then this can be used. Otherwise, one way to choose
an appropriate number is to use a test and training set process.
Essentially, this means running the process on a variety of possible
values for \emph{k} and then picking an appropriate value that performs
well.

@@

The distinguishing aspect of the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} is that it considers more than just a
document's content when constructing topics. For instance, we generally
have some information about the author and the date that a document was
created. In the case of Hansard, we know who was speaking and the date
they spoke. STM allows this additional information to affect the
construction of topics, though influencing either topical prevalence or
topical content. That said, the assumption that there is some document
generation process is the same as the LDA method, it is just that this
process now includes metadata.

@@

We primarily implement the STM on the daily-level parliamentary text
data described earlier using the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
and content to be functions of time. The choice of the number of topics
to use in the model is a situation-specific compromise. We use standard
diagnostic techniques to decide on 80 \textbf{{[}UPDATE{]}} topics. More
detail on this process is available in Appendix \textbf{{[}ADD
NUMBERING{]}}.

The illustrate the output of an STM, Figure @ref(fig:example\_topics))
shows the estimated proportion of each day summarised by ten topics for
the House of Representatives for 1901 through to 2017. \textbf{{[}RUN
AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED.{]}}

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_example} \caption{Estimated 10-topic-proportion}(\#fig:example_topics)
\end{figure}

Note that each of the states and the Commonwealth are treated
independently here. Future work could expand the model to better
understand, and allow, for correlation between them.

@@

There are many ways to statistically consider the effect of events. One
way would be to ignore the time series aspect and just group the topic
proportions by each event and then run multinomial tests for whether the
groups are different. Another would be to consider some type of
multinomial logistic regression. Options that would take advantage of
the time series nature of our data include: autoregressive moving
average (ARMA) models which are commonly used in finance to test for
structural breaks \textbf{{[}REFERENCE?{]}}; or splines could be fit
with specific knot placements and then cross validation used to compare
the RSS with a more general splines model.

@@

\subsection{Political events}\label{political-events}

\begin{quote}
\emph{When you change the government, you change the country.} Paul
Keating.
\end{quote}

Change of election

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_election} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
\end{figure}

Change of government

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_government_change} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-2}
\end{figure}

\subsection{Economic events}\label{economic-events}

Major economic changes.

Major change in economic conditions

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_economic_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-3}
\end{figure}

\subsection{Other events}\label{other-events}

\begin{quote}
\emph{Events, dear boy, events.} Attributed to Harold Macmillan.
\end{quote}

Major event such as 9/11 attacks, or economic change.

Major other changes

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_other_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-4}
\end{figure}

>>>>

\title{Nobody expects the Spanish Inquisition: The effect of events on
Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
Cochrane for their helpful suggestions. \textbf{Version as of}: 29
September 2018; \textbf{comments welcome}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }

@@

\noindent Government policy is partly driven by parliamentary discussion.
Conversely, that same discussion can indicate a government's priorities.
But major events--both expected, such as an election, and unexpected,
such as a recession or terrorist attack--can affect the course of
parliamentary discussion. In this paper, we systematically analyse how
parliamentary discussion changes in response to different types of
events in Australian history. We compile a dataset of what was said in
Australian state and federal parliaments from the mid-1800s through to
2017 based on available public records. We use a structural text model
to reduce the dimensionality of the text and to impose prior knowledge
such as correlation between days and changes over time. We then examine
the effect of various events. We find that: 1) changes of government are
associated with topic changes only when there is also a change of the
party in power; and 2) economic events, such as financial crises, have
significant and persistent effects. Our findings have implications for
how we think about the longer-term trajectory of government policy as
the media cycle becomes increasingly focused on short-term events.

@@

In this paper we examine text records of what was said in Australian
state and federal parliaments from the mid-1800s through to 2017. We use
the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
for dimensionality reduction and to impose structure such as correlation
between days and changes over time. We then examine changes at various
types of events, including: changes in government; changes in the
political environment (as defined by polling or other results); changes
in economic conditions; and other significant events (such as the 9/11
attacks or the Bali bombings).

@@

Our paper applies a topic model to a dataset of larger-scale
parliamentary text records from multiple Australian parliaments. Our
work fits into a growing literature that considers text as an input to
more usual quantitative techniques, rather than requiring separate
analysis. While using text as data has well-known shortcomings, it
allows larger-scale analysis that would not be viable using
less-automated approaches and so it can identify patterns that may
otherwise be overlooked.

@@

Following the example of the UK a daily text record called Hansard of
what was said in Australian parliaments has been made available since
their establishment.\footnote{While Hansard is not necessarily verbatim,
  it is considered close enough for text-as-data purposes. For instance,
  \citet{Mollin2008} found that in the case of the UK Hansard the
  differences would only affect specialised linguistic analysis.
  \citet{Edwards2016} examined Australia, New Zealand and the UK, and
  found that changes were usually made by those responsible for creating
  the Hansard record, instead of the parliamentarians.} Earlier work on
the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
\textbf{{[}ANOTHER REFERENCE - Maybe Frank Fisher `Reframing Public
Policy'?{]}}, often examined broader activity measures such as counts of
sitting days. This allowed for long time frames and wide comparisons.
But analysing Hansard records and their equivalents directly are an
increasingly viable and popular source of data as new methods and
reduced computational costs make larger-scale analysis easier,
complementing other measures.

The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
\citet{RheaultCochran2018} to examine ideology and party polarisation in
Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
records to examine which politicians made supportive or aggressive
statements toward other politicians between 1979 and 1990 and
\citet{PetersonSpirling2018} examined polarisation. And as digitisation
methods improve older UK records can be analysed, for instance
\citet{Dimitruk2018} considers the effect of estate bills on
prorogations in seventeenth century England. In New Zealand,
\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
and \citet{Graham2016} examined unparliamentary language between 1890
and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
congressional speech records from 1873 to 2016 to find that partisanship
has risen in the past few decades.

@@

Australian parliaments generally make their daily Hansard records
available online as PDFs and these are considered the official release.
An example of what a page of Hansard looks like is included in Appendix
\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
available in some cases.\footnote{Tim Sherratt makes these XML records
  available as a single download and also presents them in a website
  (\url{http://historichansard.net/}) that can be used to explore
  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
  records from 1998 to 2014 are available from Andrew Turpin's website,
  and from 2006 through to today from Open Australia's website. The
  records can also be downloaded from the Australian Hansard website.}
There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
available across the state and federal parliaments (Table
\ref{tab:yearsusedtable}) \textbf{{[}UPDATE NUMBERING{]}}. As with any
larger-scale data process, there are various issues with some of the
PDFs and the known ones are detailed in Appendix \textbf{{[}ADD
NUMBERING{]}}.\footnote{The NSW Legislative Council was established
  earlier than 1856, however the earlier Hansard records have not been
  through an independent OCR process and were not used in this paper.
  However, the Google Tesseract OCR engine as implemented by
  \citet{Ooms2018tesseract} provided useful data and these could be used
  in the future.}

\caption{\label{tab:yearsusedtable}Hansard records used}
\centering
\fontsize{12}{14}\selectfont
\begin{tabular}[t]{lrrr}
\toprule
Parliament & House & Years used & Number of records\\
\midrule
Commonwealth & House of Representatives & 1901 - 2017 & 7873\\
 & Senate & 1901 - 2017 & TBD\\
Queensland & Legislative Assembly & 1860 - 2017 & 9699\\
 & Legislative Council & 1860 - 1922 & 4156\\
New South Wales & Legislative Assembly & 1856 - 2017 & TBD\\
\addlinespace
 & Legislative Council & 1856 - 2017 & TBD\\
Victoria & Legislative Assembly & 1856 - 2017 & TBD\\
 & Legislative Council & 1851 - 2017 & TBD\\
Tasmania & House of Assembly & 1856 - 2017 & TBD\\
 & Legislative Council & 1856 - 2017 & TBD\\
\addlinespace
South Australia & House of Assembly & 1857 - 2017 & TBD\\
 & Legislative Council & 1840 - 2017 & TBD\\
Western Australia & Legislative Assembly & 1890 - 2017 & TBD\\
 & Legislative Council & 1832 - 2017 & TBD\\
\bottomrule
\end{tabular}
\end{table}

The formatting of the Hansard records changes between the different
parliaments and over time. We use R scripts to convert the PDFs into
daily text records.\footnote{An example of the workflow and some
  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
  NUMBERING{]}}.} These scripts are primarily based on: the
\texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
\citet{Gagolewski2018}. The functions of those packages are supported
by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
introduced at this stage because many of the records are in a two-column
format that need to be separated, and the PDF parsing is not always
accurate especially for older records. An example of the latter issue is
that `the' is often parsed as `thc'. These errors are fixed when they
occur at scale and can be identified. One way to provide assurance that
mistakes in older records are not driving the results is to analyse the
percentage of stop-words in each record over time. This details of this
are provided in Appendix \textbf{{[}ADD NUMBERING{]}} and suggest that
there is no significant difference in the quality of the parsing over
time. The \texttt{hunspell} package of \citet{Ooms2017} is also used to
help find spelling issues.

These daily records are the main level at which we consider the data in
this paper, but the daily records are also further divided into
individual-level records. Sometimes these are just short interjections
or notes that are not specific to any particular politician, such as
`Honourable members interjecting'. The high dimensional nature of text
data means that the appropriate analysis data are research-question
specific and datasets need to be tidied toward that. For instance, in
our paper interjections are not important because they do not usually
contribute much to defining the topics being discussed. But they are
interesting in their own right and \citet{Whyte2017} analysed them in a
Canadian context for the period 1926 to 2015 to find that female MPs
were more likely to be interrupted than male MPs.

Usually the disaggregation into individual-level records is done by
identifying politicians' names in particular patterns. For instance,
when Hansard is indicating that a particular person is speaking, as
opposed to being mentioned (for more on the political effect of being
mentioned see \citet{Alexander2018}), often the name is in upper case,
for instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon;
or are next to some title within brackets. There is substantial
variation in how the person making a statement is identified. Again some
error is introduced at this stage because of inconsistencies over time
and between the parliaments. There is considerable variance but on
average each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
records, resulting in roughly 15 million rows \textbf{{[}UPDATE{]}}
across the state and federal parliaments.

Text usually needs to be pre-processed before topic models can be used.
The specific steps that we take are to remove numbers and punctuation
and to change all the words to lower case. Then the sentences are
deconstructed and each word considered individually. In addition to the
packages already mentioned, in this step the R scripts to do this use
the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
\textbf{{[}Need to bundle\_ngrams i.e.~New Zealand is new\_zealand.{]}}

@@

Data from other sources are useful to complement the parliamentary text
data. For instance, although the name, party, and division represented
are contained in Hansard records they are inconsistent. Also non-Hansard
information about the politicians informs our analysis. This includes:
date of birth and date of death; sex; date of entry to parliament and
exit from parliament; some aspects of their pre- and post-parliamentary
career; some aspects of their parliamentary career, such as ministry
appointments; and electoral information such as primary and
two-party-preferred results.

The main sources for this additional supplementary information are the
handbooks supplied by the various parliaments. However these had many
errors and were supplemented by data from the Australian Dictionary of
Biography and Wikipedia.\footnote{An example of the additional
  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}.} The
source for the electoral results is the Australian Electoral Commission
and Adam Carr's Australian Election Archive.

@@

The main model that we use in this paper is the Structural Topic Model
(STM) as implemented by the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. In a similar way to
\citet{MuellerRauh2018}, we use these topics to analyse the effect of
various events. In Appendix \textbf{{[}ADD NUMBERING{]}}, we include an
alternative approach that follows \citet{Taddy2015} by using word2vec,
which more closely uses words, rather than topics, as an input.

The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section we provide a brief overview of
both the LDA model and the STM. We consider the outputs of the topic
model as reduced dimension inputs that can be analysed.

@@

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics. More generally, the
LDA topic model works by considering each document as having been
generated by some probability distribution over topics. Similarly, each
topic could be considered a probability distribution over terms. To
choose the terms used in each document the speaker picks terms from each
topic in the appropriate proportion. Figures
\ref{fig:topicsoverdocuments} and \ref{fig:topicsoverterms} in Appendix
\textbf{{[}ADD NUMBERING{]}} illustrates an example with five topics,
two documents, and ten terms.

@@

Gibbs sampling or the variational expectation-maximization algorithm can
be used to approximate the posterior. A summary of these approaches is
provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The choice of the
number of topics, \emph{k}, drives the results and must be specified
\emph{a priori}. If there is a strong reason for a particular number,
then this can be used. Otherwise, one way to choose an appropriate
number is to use cross validation.

@@

The distinguishing aspect of the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} is that it considers more than just a
document's content when constructing topics. For instance, we generally
have some information about the author and the date that a document was
created. In the case of Hansard, we know who was speaking and the date
they spoke. The STM allows this additional information to affect the
construction of topics, though influencing either topical prevalence or
topical content. That said, the assumption that there is some document
generation process is the same as the LDA method, it is just that this
process now includes metadata.

@@

We primarily implement the STM on the daily-level parliamentary text
data described earlier using the \texttt{stm} R package of
\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
and content to be functions of time. The choice of the number of topics
to use in the model is a situation-specific compromise. We use standard
diagnostic techniques with cross validation to decide on 80
\textbf{{[}UPDATE AS APPROPRIATE{]}} topics. More detail on this
selection process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.

Figure \ref{fig:exampletopics} illustrates an output of the STM. This
illustrative model only considers data from the House of Representatives
between 1901 and 2017. It shows how each day's parliamentary discussion
can be allocated to one of ten topics and highlights how the prominence
of these topics changes over time. \textbf{{[}RUN AND GRAPH AN ACTUAL
10-TOPIC MODEL - THESE DATA ARE JUST SUMMED FROM THE GENERAL ONE!.{]}}

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_example} \caption{Estimated 10-topic-proportion}\label{fig:exampletopics}
\end{figure}

@@

There are many ways to statistically consider the effect of events. One
way would be to ignore the time series aspect and just group the topic
proportions by each event and then run multinomial tests for whether the
groups are different. Another would be to consider some type of
multinomial logistic regression. Options that would take advantage of
the time series nature of our data include: autoregressive moving
average (ARMA) models which can be used to test for structural breaks
\textbf{{[}REFERENCE?{]}}; or splines could be fit with specific knot
placements and then cross validation used to compare the RSS with a more
general splines model.

\textbf{{[}MONICA - LOOK AT THESE OR OTHER OPTIONS AND DECIDE ON A WAY.
NEEDS TO ALLOW FOR SHORT AND LONG RUN AND ALSO ALLOW COINCIDENCE OF
EVENTS. WE ONLY CONSIDER 20 TOPICS BELOW, BUT THAT'S UNDERDONE AND THE
METHODS NEED TO ALLOW FOR MORE.{]}}

We currently consider events in two ways. The first is graphically,
grouping each of the daily topic proportions by the events and isolating
the topics. This illustrates the differences between the topics. The
second is by including incrementing variables in the prevalence metdata.
This groups each day by events and we can then conduct significance
tests. Unfortunately both of these do not consider short-term effects.

\textbf{{[}Use tf-idf between them as illustrative instead? Use that
other measure of difference?{]}}

@@

We are interested in considering the effect of various events on what is
talked about in Australia's parliaments. Each of those parliaments are
treated independently here. Future work could expand the model to better
understand, and allow, for correlation between them.

We consider four types of events and group the day's topic proportions
by these events. One unfortunate effect of this is that we only allow an
event to have a long-run effect and ignore short-run effects. Another is
that we ignore coincidence of events.

Figure \ref{fig:electionsevents} shows the grouping by election. If
elections had significant effects on the discussion in parliament then
there would be considerable change between groups. However changes
generally appear to be longer-term rather than election to election.

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_election} \caption{Topic proportions grouped by elections}\label{fig:electionsevents}
\end{figure}

Figure \ref{fig:governmentevents} shows the grouping by government. This
can be different to election groupings, for instance, the change from
the Rudd to Gillard governments happened without an election. Similarly,
John Howard's three terms are all considered the one government for our
purposes.

Here we see much more difference between adjacent events. This suggests
that new governments tend to talk about different topics than the
government they replace.

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_government_change} \caption{Topic proportions grouped by government}\label{fig:governmentevents}
\end{figure}

Figure \ref{fig:economicevents} shows the grouping by major economic
changes. There are considerable changes between adjacent events.

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_economic_changes} \caption{Topic proportions grouped by economic events}\label{fig:economicevents}
\end{figure}

Figure \ref{fig:otherevents} shows the grouping by major other events,
such as the 9/11 attacks.

\begin{figure}
\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_other_changes} \caption{Topic proportions grouped by other events}\label{fig:otherevents}
\end{figure}

Another way to consider the effect of events is by including
incrementing variables in the prevelance metadata. This then gets
included in the topic modelling and the significance to each topic can
be computed. Table \ref{tab:dodgysignificances} summarises these by the
type of dummy and the topic. At the five per cent level the events that
we consider were significant for eight topics. This significance tended
to be correlated, especially for economic and other events.
